### 2024-01-04 tesis_Ashish/Chapter2/chapter2.tex
Updated thesis 4 Jan 2024

The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-15-001}\cite{CMS-PAS-LUM-16-001}. A lumi section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable. The luminosity delivered during each of these lumi sections can vary, leading to different levels of activity in the detector.

>>>>

The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-16-001}. A lumi section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable. The luminosity delivered during each of these lumi sections can vary, leading to different levels of activity in the detector.
